\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Charlie McLaughlin} \\ \vspace{1pt}
    \small 902-740-0842 $|$ 
    \href{mailto:charliermclaughlin@gmail.com}{\underline{charliermclaughlin@gmail.com}} $|$ 
    \href{https://linkedin.com/in/charlie-mclaughlin-s13/}{\underline{linkedin.com/in/charlie-mclaughlin-s13}} $|$
    \href{https://github.com/CharlieIQ}{\underline{github.com/CharlieIQ}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dalhousie University}{Halifax, NS}
      {Bachelor's of Computer Science (GPA 4.01)}{September 2023 -- Present}
    \resumeSubheading
      {Yarmouth Consolidated Memorial High School}{Yarmouth, NS}
      {High School Diploma (98.0\% Average)}{September 2019 -- June 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{May 2025 -- July 2025}
      {Cognizant}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Developed a full-stack chat bot application to assist technical support teams using the Google Cloud Platform}
        \resumeItem{Led the front end development in ReactJS, and assisted the backend development using the Python Flask framework}
        \resumeItem{Set up CI/CD pipelines to automate testing using Vitest and deployment through Google Cloud Build}
        \resumeItem{Participated in Scrum ceremonies to support Agile delivery and team alignment.}
      \resumeItemListEnd

    \resumeSubheading
      {GIS Technician}{February 2023 -- August 2024}
      {Town of Yarmouth}{Yarmouth, NS}
      \resumeItemListStart
        \resumeItem{Co-developed a GIS-based web map featuring 400+ accessible locations across Yarmouth County using QGIS/ArcGIS.}
        \resumeItem{Managed version control and collaboration using Git.}
        \resumeItem{The project was deployed using HTML \& JavaScript and is being widely used by residents of the county.}
    \resumeItemListEnd

    \resumeSubheading
      {Software \& Security Intern}{July 2022 -- August 2023}
      {IBM}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Developed and deployed a company wide acronym bot using JavaScript, PHP, and SQL in collaboration with frontend and project management teams.}
        \resumeItem{Enhanced security event documentation and classified incidents for a large scale SIEM product.}
        \resumeItem{Automated SIEM product updates using Python, improving response efficiency.}
        \resumeItem{Utilized GitHub for team collaboration, with the bot project now in active company use.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/CharlieIQ/agentic-devteam-ai} {Agentic AI Devteam}} $|$ \emph{ReactJS, CrewAI, Python}}{July 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed an agentic AI-powered software team using CrewAI to automate full-stack app prototyping.}
            \resumeItem{Created a Python Flask server to manage frontend API calls to the AI development team.}
            \resumeItem{Designed a React-based UI for users to submit project requirements and receive auto generated code.}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{\href{https://github.com/CharlieIQ/piggle} {Piggle}} $|$ \emph{React, CSS, Firebase, Cloud Firestore}}{February 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and developed an interactive browser based puzzle game using React.}
        \resumeItem{Implemented Firestore to manage player accounts, levels, and leaderboard data in real time.}
        \resumeItem{Developed a functional level editor, and a level browser dashboard for user created content.}
      \resumeItemListEnd
      \resumeProjectHeading        {\textbf{\href{https://charlieiq.github.io/accessibility_mapping_project/} {Yarmouth County Accessibility Map}} $|$ \emph{JavaScript, HTML, CSS, QGIS}}{February 2023 -- August 2024}
          \resumeItemListStart
            \resumeItem{Created a map of all accessible points in Yarmouth County Nova Scotia.}
            \resumeItem{Used QGIS and ArcGIS for plotting the points and Git for project management.}
            \resumeItem{Created an interactive front end website to display the map using HTML and JavaScript.}
            \resumeItem{Map is used by residents with accessibility needs in Yarmouth County, and tourists coming to the area.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, C, SQL, HTML/CSS} \\
     \textbf{Frameworks \& Libraries}{: React, Node.js, Flask, Tailwind, JUnit, Jest, Vitest, pandas, NumPy } \\
     \textbf{Developer Tools}{: Git, GCP, Firebase, VS Code, PyCharm, IntelliJ, MySQL} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
